---
output: html_document
editor_options: 
  chunk_output_type: console
---

---
title: "Jaccard Index Analysis"
author: "Ammar Sabir Cheema"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# loading libraries
```{r}
library(pheatmap)
library(RColorBrewer)
```
# Read the cluster markers for first dataset
```{r}
aa <- list.files(path = "/home/user/jac_analysis/", pattern = "merad", all.files = TRUE,
            full.names = FALSE, recursive = FALSE,
            ignore.case = FALSE, include.dirs = FALSE)
 print(aa)

 dataset_merad <- lapply(aa, read.table)
 names(dataset_merad) <- list.files(path="/home/user/jac_analysis/", pattern = "merad", full.names=FALSE)

 names(dataset_merad) <- sub("cluster", "C", names(dataset_merad))
 names(dataset_merad) <- sub("merad_sc_data_only_cDC1.txt", "MD", names(dataset_merad))
 names(dataset_merad)

# I only keep the gene names. 
 for (i in 1:length(dataset_merad)) {
   dataset_merad[[i]] <- rownames(dataset_merad[[i]])
}
``` 
 
# Read the cluster markers for second dataset
```{r}
bb <- list.files(path = "/home/user/jac_analysis/", pattern = "wo_M1", all.files = TRUE,
            full.names = FALSE, recursive = FALSE,
            ignore.case = FALSE, include.dirs = FALSE)
 
 
 dataset_ghita <- lapply(bb, read.table)
 names(dataset_ghita) <- list.files(path="/home/user/jac_analysis/", pattern = "wo_M1", full.names=FALSE)
 names(dataset_ghita) <- sub("cluster", "C", names(dataset_ghita))
 names(dataset_ghita) <- sub("wo_M1_wo_conta.txt", "GD", names(dataset_ghita))
 names(dataset_ghita)


# I only keep the gene names. 
for (i in 1:length(dataset_ghita)) {
  dataset_ghita[[i]] <- rownames(dataset_ghita[[i]])
}
```

# Compute the size of intersection between list of genes of pairs of different clusters of the tissues
# and compute the Jaccard index for each pair of clusters. Store both information in two different dataframes

```{r}
jaccard_index_df = data.frame()
intersection_df = data.frame()
for(i in 1:length(dataset_merad)) {
  jaccard_index_set = vector()
  details_set = vector()
  for(j in 1:length(dataset_ghita)) {
    jaccard_index = length( intersect( dataset_merad[[i]], dataset_ghita[[j]])) / length( unique( c( dataset_merad[[i]], dataset_ghita[[j]])))
    jaccard_index_set = append( jaccard_index_set, jaccard_index)
    details_set = append( details_set, length( intersect( dataset_merad[[i]], dataset_ghita[[j]])))
  } 
  jaccard_index_df = rbind( jaccard_index_df, jaccard_index_set)
  intersection_df = rbind( intersection_df, details_set)
}
names( jaccard_index_df) = names(dataset_ghita)
row.names( jaccard_index_df) = names(dataset_merad)
names( intersection_df) = names(dataset_ghita)
row.names( intersection_df) = names(dataset_merad)
```

# Display the data.frame of jaccard indexes as a heatmap
```{r}
break_list = seq(0, 0.4, by = 0.05)
pheatmap::pheatmap(
  jaccard_index_df,
  color = colorRampPalette(brewer.pal(n = 9, name = "Blues"))(length( break_list)),
  cellwidth =40, cellheight =30,
  fontsize = 12,
  show_rownames = T, show_colnames = T,
  angle_col = 45,
  breaks = break_list,
  display_numbers = matrix( paste0( as.matrix( intersection_df), " (", 100*signif( as.matrix( jaccard_index_df), 2), "%)"), ncol = length(dataset_ghita)),
  cluster_rows = FALSE, cluster_cols = FALSE,
  treeheight_row = 0, treeheight_col=0
)
```
